R Notebook

### 2023-04-07 Charuco_DLT/rearrange_point_for_easywand.Rmd
Doing charuco calibrations

Fill in the name of the output CSV file from `detect_charuco.ipynb`.
```{r}
detections <- read_csv("/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09/boards.csv") |> 
  select(-`...1`)
```

Fill in the directory that has the video files and the names of each video.
```{r}
videodir <- '/Users/Ben/Desktop/Charuco_DLT/charuco_boards/2023_02_09'
camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
camfiles <- map(camfiles, ~ file.path(videodir, .x))
```

@@

And save out the CSV.
```{r}
write_csv(ptsforeasywand, "/Users/Ben/Desktop/Charuco_DLT/2023_02_XX_calibrationcharuco_xypts.csv")
```

>>>>

Fill in the name of the output CSV file from `detect_charuco.ipynb`.
```{r}
detections <- read_csv("/Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06/boards.csv") |> 
  select(-`...1`)
```

Fill in the directory that has the video files and the names of each video.
```{r}
videodir <- '//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06'
camfiles <- c('checkerboard_V1.mp4','checkerboard_V2.mp4')
camfiles <- map(camfiles, ~ file.path(videodir, .x))
```

@@

And save out the CSV.
```{r}
write_csv(ptsforeasywand, "//Users/Ben/Desktop/Fish-Midline-Processer/Charuco_DLT/charuco_boards/2023_04_06/2023_04_06_calibrationcharuco_xypts.csv")
```
